Mendelian randomization for causal inference in Genome-wide association studies

### 2022-01-31 mr-review.Rmd
reworded a sentence
added csl

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
output: 
  - bookdown::html_document2
  - bookdown::word_document2
---

@@

Great interest has developed in inferring causal relationships between complex 
traits in observational human genetics studies.

Genome-wide association studies (GWAS) present unique opportunities for 
discovery of causal relationships via mendelian randomization.

@@

Now, GWAS and Mendelian randomization for Biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller sample sizes.

@@

Investigators have found that combining information from multiple  related traits can lead to more informative MR results.

>>>>

---
title: "Mendelian randomization for causal inference in Genome-wide association studies"
author: "Frederick J. Boehm & Xiang Zhou"
date: "`r lubridate::now()`"
bibliography: exported.bib
csl: elsevier-with-titles.csl
output: 
  - bookdown::html_document2
  - bookdown::word_document2
---

@@

Great interest has developed in inferring causal relationships between complex 
traits in observational human genetics studies. Throughout the manuscript, we 
use the term "complex trait" to refer to a trait that doesn't appear to be 
inherited in a Mendelian fashion. Typically, traits such as gene expression levels
are inherited in a polygenic manner, with many genes influencing the trait.

Genome-wide association studies (GWAS) present unique opportunities for 
discovery of causal relationships via mendelian randomization. A genome-wide association study 
interrogates millions of single nucleotide polymorphisms (SNPs) to infer which affect the trait. A 
SNP is a genetic marker defined by nucleotide base identity at a single genomic position.

@@

Now, GWAS and Mendelian randomization for biobank-scale data offer the possibility
of discovering even more causal relationships among complex traits. The large
sample sizes in biobank studies offer the possibility of uncovering associations of modest strength 
that might be undetectable in smaller sample sizes.

@@

Investigators have found that combining information from multiple related traits can lead to richer MR results.
